GxHash: A High-Throughput, Non-Cryptographic Hashing Algorithm Leveraging Modern CPU Capabilities

### 2023-10-09 article/article.tex
Add more benchmark results

\begin{table}[H]
\centering
\begin{tabular}{|l|r|r|r|r|}
\hline
\textbf{Function for MarkovWords dataset} & \textbf{Collisions} & \textbf{Bits Distribution} & \textbf{Distribution} & \textbf{Avalanche} \\
\hline
Int32 GxHash0(64)                & 0,0136\% & 0,001082  & 0,000002 & 0,00319 \\
Int32 GxHash0(1000)              & 0,0119\% & 0,000894  & 0,000002 & 0,0034 \\
Int32 HighwayHash(64)            & 0,0123\% & 0,000809  & 0,000002 & 0,00048 \\
Int32 HighwayHash(1000)          & 0,0117\% & 0,00092   & 0,000002 & 0,00078 \\
Int32 T1ha(64)                   & 0,0111\% & 0,000803  & 0,000002 & 0,00064 \\
Int32 T1ha(1000)                 & 0,0123\% & 0,001175  & 0,000002 & 0,00135 \\
UInt32 XxHash(64)                & 0,0106\% & 0,000766  & 0,000002 & 0,00046 \\
UInt32 XxHash(1000)              & 0,01\%   & 0,000892  & 0,000002 & 0,00021 \\
UInt32 Fnv1a(64)                 & 0,0122\% & 0,000998  & 0,000002 & 0,08585 \\
UInt32 Fnv1a(1000)               & 0,0127\% & 0,000993  & 0,000002 & 0,08143 \\
UInt32 Crc(64)                   & 0,0124\% & 0,000965  & 0,000002 & 0,02467 \\
UInt32 Crc(1000)                 & 0,0123\% & 0,000708  & 0,000002 & 0,00499 \\
\hline
\end{tabular}
\caption{Your Table Caption Here}
\label{tab:my_label}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{throughput.png}
\caption{Throughput Benchmark Results}
\label{fig:benchmark-throughput}
\end{figure}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{|l|r|r|r|r|}
\hline
\textbf{Function for MarkovWords dataset} & \textbf{Collisions} & \textbf{Bits Distribution} & \textbf{Distribution} & \textbf{Avalanche} \\
\hline
UInt32 GxHash0(64)                & 0,0136\% & 0,001082  & 0,000002 & 0,00319 \\
UInt32 GxHash0(1000)              & 0,0119\% & 0,000894  & 0,000002 & 0,0034 \\
UInt32 HighwayHash(64)            & 0,0123\% & 0,000809  & 0,000002 & 0,00048 \\
UInt32 HighwayHash(1000)          & 0,0117\% & 0,00092   & 0,000002 & 0,00078 \\
UInt32 T1ha(64)                   & 0,0111\% & 0,000803  & 0,000002 & 0,00064 \\
UInt32 T1ha(1000)                 & 0,0123\% & 0,001175  & 0,000002 & 0,00135 \\
UInt32 XxHash(64)                & 0,0106\% & 0,000766  & 0,000002 & 0,00046 \\
UInt32 XxHash(1000)              & 0,01\%   & 0,000892  & 0,000002 & 0,00021 \\
UInt32 Fnv1a(64)                 & 0,0122\% & 0,000998  & 0,000002 & 0,08585 \\
UInt32 Fnv1a(1000)               & 0,0127\% & 0,000993  & 0,000002 & 0,08143 \\
UInt32 Crc(64)                   & 0,0124\% & 0,000965  & 0,000002 & 0,02467 \\
UInt32 Crc(1000)                 & 0,0123\% & 0,000708  & 0,000002 & 0,00499 \\
\hline
\end{tabular}
\caption{Your Table Caption Here}
\label{tab:my_label}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{quality-markov.png}
\caption{Distribution map for markov dataset}
\label{fig:quality-sequential}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{throughput.png}
\label{fig:benchmark-throughput}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{throughput-gcp.png}
\label{fig:benchmark-throughput-gcp}
\end{figure}
